Predicting the 2024 US Presidential Election: A Polling-Based Forecast

### 2024-11-04 paper/paper.qmd
Modify the discussion
Signed-off-by: FrankFU323 <tianrui.fu@mail.utoronto.ca>

\newpage
# Introduction {#sec-data}

@@

The predictive models deployed in our study delineate a subtle yet pivotal dynamic: economic indicators and significant public events exert substantial influence on voter behavior as elections approach. The Bayesian analysis reveals a close support rate between Donald Trump (46.87%) and Kamala Harris (48.50%), highlighting an electorate acutely responsive to shifts in economic sentiment and public perception. This responsiveness is intensified by the fact that nearly 41% of pollsters show varying support levels for Trump, underscoring a voter sentiment that is not merely divided but remarkably fluid. This data suggests that electoral outcomes can pivot rapidly following major economic updates or notable public engagements by candidates, potentially reshaping the electoral narrative almost instantaneously.

>>>>

\newpage
# Introduction {#sec-introduction}

@@

The predictive models deployed in our study delineate a subtle yet pivotal dynamic: economic indicators and significant public events exert substantial influence on voter behavior as elections approach. The Bayesian analysis reveals a close support rate between Donald Trump (46.87%) and Kamala Harris (48.50%), highlighting an electorate acutely responsive to shifts in economic sentiment and public perception. This responsiveness is intensified by the fact that nearly 31% of pollsters show varying support levels for Trump, underscoring a voter sentiment that is not merely divided but remarkably fluid. This data suggests that electoral outcomes can pivot rapidly following major economic updates or notable public engagements by candidates, potentially reshaping the electoral narrative almost instantaneously.
